Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-09-11 stp/paper_aaai/main.tex
2 words in intro

A standard approach to tackle this problem is to design a common ontology and to construct source descriptions which specify mappings between the sources and the ontology \cite{doan2012principles}.
In this paper, we tackle the data integration problem consisting in automatically mapping a new relational data source onto a user provided ontology.
To do so, we develop a new tool that automatically builds a semantic model which describes a relational data source in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.

>>>>

A standard approach to tackle this problem is to design a common ontology and to construct source descriptions which specify mappings between the sources and the ontology \cite{doan2012principles}.
In this paper, we approach the data integration problem consisting in automatically mapping a new relational data source onto a user provided ontology.
To do so, we develop a new system that automatically builds a semantic model which describes a relational data source in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
